---
title: "Purrr"
output: html_document
date: "2024-11-05"
---

```{r setup, include=FALSE}
library(purrr)
library(dplyr)
```

Pre-Reading and In-Class Demo

```{r}
tmp_dat <- data.frame(
  x = 1:5,
  y = 6:10
)

map_dbl(.x = tmp_dat, .f = mean)

tmp_dat |>
  map_dbl(mean)

x <- list(1:5, c(1:10, NA))
map_dbl(.x = x, .f = mean, na.rm = T)

unique(mtcars$cyl) 
by_cyl <- split(mtcars, mtcars$cyl)
length(by_cyl)

by_cyl |>
  map(.f = ~ lm(mpg ~ wt, data = .x))

lm.fit <- lm(mpg ~ wt, data = .x)

by_cyl |>
  map(.f = ~ lm(mpg ~ wt, data = .x)) |>
  map(coef) |>
  map_dbl(2)
```

walk() function - useful for reading in a lot of CSV files when you don't want any output/don't want anything returned

```{r}
df <- data.frame(
  x = 1:3,
  y = 6:4
)

map(df, ~ .x *2)

# in we want output to be a data frame using modify():
modify(df, ~ .x *2)
```

Class Activity

Part 1
```{r}
map_dbl(mtcars, mean)
map_dbl(mtcars, sd)
map(mtcars, range)
```

Part 2
```{r}
as.data.frame(map_if(mtcars, ~ mean(.x) < 20, ~.x * 100))
```

Part 3
```{r}
as.data.frame(map_if(mtcars, .p = ~mean(.x) > 20, .f = ~log(.x), .else = ~sqrt(.x)))
```

Part 4

First, define a function that assigns each row a fuel efficiency category based on mpg:

“High” if mpg > 25
“Medium” if mpg is between 20 and 25
“Low” if mpg < 20

```{r}
fe <- function(row) {
    mpg <- row["mpg"]
    if (mpg > 25) {
    "High"
  } else if (mpg >= 20) {
    "Medium"
  } else {
    "Low"
  }
}

mtcars$fuel_efficiency <- map_chr(asplit(mtcars,1), .f = fe)
mtcars

by_fe <- split(mtcars, mtcars$fuel_efficiency)
map(by_fe, .f = ~mean(.x[,c("hp","wt","qsec")]))
map(by_fe, .f = ~mean(c(.x$hp,.x$wt)))
```

